Meta-analysis

### 2019-09-14 01_Meta-analysis_experiments.Rmd
Reformat R code chunks

```{r}
knitr::kable(
   cbind(Acronym = c("SF", "Ti", "AX", "Ca"),
         Expected_Fungicide = c("Sulphur", "Tilt", "Amistar Xtra", "Carbendazim"),
         Active_Ingredient = c("Sulphur", "Propiconazole", "Azoxystrobin and Cyproconazole", "Carbendazim")
   )
)
```

@@

kable(PM.dat %>%
   group_by(Trial_ref, Year, Location, trial_design, Replicates, planting_date, emergence_date, first_sign_disease) %>%
   summarise(Treatments = length(E_treatment)),
   caption = "Description of Experiments") %>%
   kable_styling(fixed_thead = T, full_width = T) %>%
   scroll_box(width = "900px", height = "500px")

PM.dat$Trial_ref <- factor(PM.dat$Trial_ref)
PM.dat$Location <- factor(PM.dat$Location)
PM.dat$Year <- factor(PM.dat$Year)
PM.dat$host_genotype <- factor(PM.dat$host_genotype)
PM.dat$Fungicide <- factor(PM.dat$Fungicide)
PM.dat$Trade_name <- factor(PM.dat$Trade_name)

## Experimental locations
Experimental locations where data was sufficient to include in meta-analysis
```{r Experiment_locations}

experiment_sites <- data.frame(
   location = c("Hermitage", "Kingaroy research station","Gatton", "Emerald Agricultural College"),
   lat = c(-28.215 ,-26.58,-27.56,-23.54),
   lon = c(152.1003,151.83,152.32,148.19)
)

 leaflet() %>%
    addProviderTiles("Esri.WorldTopoMap") %>%
    addMarkers(lng = experiment_sites$lon, lat = experiment_sites$lat)
# head(silo_gatton_Tmax)

>>>>

```{r}
knitr::kable(cbind(
   Acronym = c("SF", "Ti", "AX", "Ca"),
   Expected_Fungicide = c("Sulphur", "Tilt", "Amistar Xtra", "Carbendazim"),
   Active_Ingredient = c(
      "Sulphur",
      "Propiconazole",
      "Azoxystrobin and Cyproconazole",
      "Carbendazim"
   )
))
```

@@

kable(
   PM.dat %>%
      group_by(
         Trial_ref,
         Year,
         Location,
         trial_design,
         Replicates,
         planting_date,
         emergence_date,
         first_sign_disease
      ) %>%
      summarise(Treatments = length(E_treatment)),
   caption = "Description of Experiments"
) %>%
   kable_styling(fixed_thead = TRUE, full_width = TRUE) %>%
   scroll_box(width = "900px", height = "500px")

PM.dat$Trial_ref <- factor(PM.dat$Trial_ref)
PM.dat$Location <- factor(PM.dat$Location)
PM.dat$Year <- factor(PM.dat$Year)
PM.dat$host_genotype <- factor(PM.dat$host_genotype)
PM.dat$Fungicide <- factor(PM.dat$Fungicide)
PM.dat$Trade_name <- factor(PM.dat$Trade_name)
```

## Experimental locations

Experimental locations where data was sufficient to include in meta-analysis.

```{r Experiment_locations}
experiment_sites <- data.frame(
   location = c(
      "Hermitage",
      "Kingaroy Research Station",
      "Gatton",
      "Emerald Agricultural College"
   ),
   lat = c(-28.215 , -26.58, -27.56, -23.54),
   lon = c(152.1003, 151.83, 152.32, 148.19)
)

leaflet() %>%
   addProviderTiles("Esri.WorldTopoMap") %>%
   addMarkers(lng = experiment_sites$lon, lat = experiment_sites$lat)
# head(silo_gatton_Tmax)
```
